---
title: "Report"
author: "Rong Li"
date: "2020/12/12"
output: pdf_document
fig_caption: yes
header-includes:
  - \usepackage{placeins}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pacman::p_load(knitr, png, grid, magrittr, tidyr, dplyr, lubridate, ggpubr, gridExtra)
knitr::knit_hooks$set(plot = function (x, options) {
  float_correct <- function(f, y, opts)  {
    if (is.null(opts$regfloat) || opts$regfloat==FALSE)
      paste0(f(y, opts), "\n\n\\FloatBarrier\n")
    else
      f(y, opts)
  }
  if (!is.null(options$out.width) || !is.null(options$out.height) ||
      !is.null(options$out.extra) || options$fig.align != "default" ||
      !is.null(options$fig.subcap)) {
    if (is.null(options$fig.scap))
      options$fig.scap = NA
    return(float_correct(knitr:::hook_plot_tex, x, options))
  }
  return(float_correct(knitr:::hook_plot_md_base, x, options))
})
```

## Introduction

The COVID-19 pandemic has had a devastating effect on the economy in the United States. In early March 2020, the first lockdowns began and the stock market plunged. After this initial reaction, however, the market recovered.  
In this assignment, we assume an intial position of \$250,000 in cash on 2020-07-01 and invest 6 stocks using investment advice before 1 July from ETF. We track the value of our portfolio using last close prices through the fall to 2020-12-01. At the end of 2020-12-01, we have a position of \$495,201 in cash.  
The goal of the final project is only to demonstrate our skill.

\newpage
## Data
In this part, we illustrate how to download and clean the data we need. And the first several rows of our dataset are displayed.   

### Preparation
- We use tq_exchange() to collect the name of all stocks from three stock exchanges (AMER, NASDAQ, NYSE). This dataset has 7535 rows (7535 stocks) and 7 columns.  

```{r}
load("/Users/amelia/Documents/mssp/MA615/MA615_FinalProject/MA615_FinalProject/stocklist.RData")
kable(stocklist[1:3,])
```

- Then we use tq_get() to download price of all stocks form 2020-07-01 to 2020-11-30. When we continue to download data on 2020-12-01, the connection of tq_get() failes. This dataset contains 654984 rows and 8 columns.  

```{r}
load("/Users/amelia/Documents/mssp/MA615/MA615_FinalProject/MA615_FinalProject/stockprice.RData")
kable(stockprice[1:3,])
```

- So, we search closing price on 2020-12-01 of the six stocks we are interested in one by one on [**YAHOO**](https://finance.yahoo.com/) website.   

```{r}
addrevenue <- data.frame(date = "2020-12-01", 
                         ZM = 406.31, 
                         CTVA = 38.31, 
                         PINS = 68.21, 
                         UBER = 49.63, 
                         MRNA = 141.01, 
                         PENN = 70.03)
kable(addrevenue)
```

- Finally we obtain two big datasets and six closing prices on 2020-12-01.  


### Cleaning
- We eliminate the stocks without full trading days.  

```{r, result = "hide"}
# delete NAs
# stocklist %<>% na.omit()
stockprice %<>% na.omit()

# filter the stock don't have full trading days
a <- stockprice %>% group_by(symbol) %>% summarise(count = sum(year(date) > 2019))
a %<>% filter(count == 106)
stocklist %<>% filter(symbol %in% a$symbol)
stockprice %<>% filter(symbol %in% a$symbol)
rm(a)
```

\newpage
## Investment
In this part, we use online investment advice that was available at the beginning of July 2020 to make investment decisions and then track our investments through the fall until 1 December.  

### Online Advice
We search some big fund companies and look at their top ten holdings on [**ETF**](https://www.etf.com/channels/ipo) website.  

```{r, fig.cap="These three pictures show the top ten holdings of three fund(First Trust U.S. Equity Opportunities ETF, Renaissance IPO ETF and First Trust International Equity Opportunities ETF).", fig.height = 3.5}
p1 <- readPNG("/Users/amelia/Documents/mssp/MA615/MA615_FinalProject/MA615_FinalProject/1.png")
grid.raster(p1)
```

### Portfolio
From figure 1, we choose 6 companies that we are interested in and give them different weights. Assume an initial position of $250,000 in cash starting on 1 July 2020. After buying these 6 stocks, we still have \$1.59. The holdings are listed in here:  

```{r}
# find the stock I want to hold
melist <- stocklist %>% filter(symbol %in% c("MRNA", "ZM", "UBER", "PINS", "PENN", "CTVA"))
#mestock$company
# "Moderna, Inc."                   "Penn National Gaming, Inc."     
# "Zoom Video Communications, Inc." "Corteva, Inc."                  
# "Pinterest, Inc."                 "Uber Technologies, Inc."

# find the price of six stocks
meprice <- stockprice %>% filter(symbol %in% melist$symbol)

# find the price on 2020-07-01
mepricefirst <- meprice %>% filter(date == "2020-07-01")
#unique(mepricefirst$symbol)
# "ZM"   "CTVA" "PINS" "UBER" "MRNA" "PENN"

# I have $250000 in July 1st
shareratio <- c(0.2, 0.1, 0.1, 0.2, 0.3, 0.1) * 250000
shareset <- floor(shareratio/mepricefirst$close)
#round(sum(shareratio - shareset * mepricefirst$close), 2)
shareset[1] <- shareset[1] + 1
shareset[3] <- shareset[3] + 1
shareset[5] <- shareset[5] + 1
rest <- round(sum(shareratio - shareset * mepricefirst$close), 2)


shareratio <- (shareset * mepricefirst$close) / sum(shareset * mepricefirst$close)
mepricefirst %<>% mutate(share = shareset, amount = shareset * mepricefirst$close, percent = paste(round(shareratio*100), "%"))

df <- mepricefirst[order(mepricefirst$percent, decreasing = TRUE), c(1, 9, 10, 11)]
df$company <- c("Maderna", "Zoom", "Uber", "Corteva", "Pinterest", "Penn")
df %<>% select(symbol, company, share, amount, percent)
df2 <- data.frame(company = "Total", share = " ", amount = sum(df$amount), percent = paste(100, "%"))
rbind(df[, 2:5], df2) %>% kable()
```

Then we use donut chart to see the proportions of each sector.  

```{r, fig.cap = "This shows the proportions of each sector.", fig.height=3}
#some donut graphs
df$labs <- paste0(df$company, " (", df$percent, ")")

df3 <- melist[-5,] #delete PINS
df3 %<>% left_join(df, by = "symbol")
df3 %<>% select(sector, amount, percent)
df3$amount[3] <- 75014.81 
df3$percent[3] <- "30 %"
df3$labs <- paste0(df3$sector, " (", df3$percent, ")")
p3 <- ggdonutchart(df3, "amount",
             label = "labs", 
             lab.pos = "out", 
             fill = "sector",
             lab.adjust = 0,
             lab.font = c(4, "bold", "grey"),
             color = "white",
             palette = "Greens") + 
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5)) + 
  coord_polar(theta = "y", start = 0, clip = "off")
p3
```

As we can see from Figure2, the investment is concentrated in technology and health care sectors.  

### Result
Now we hold 1218 shares of Maderna, 193 shares of Zoom, 1643 shares of Uber, 924 shares of Corteva, 1074 shares of Pinterest and 783 shares of Penn National Gaming and \$1.59 in cash. We track our investments using last close prices through the fall to 2020-12-01 and calculate the value of our portfolio every day.

```{r, fig.cap = "This shows the asset value from 2020-07-01 to 2020-12-01", fig.height=3.5, fig.width=5.5}
# calculate the revenue every day
#unique(meprice$symbol)
# "ZM"   "CTVA" "PINS" "UBER" "MRNA" "PENN"
revenue <- meprice[, c(1, 2, 6)] %>% pivot_wider(names_from = symbol, 
                                   values_from = close)
# forget to download data on 2020-12-01, add the close price of the six stocks
addrevenue <- data.frame(date = "2020-12-01", 
                         ZM = 406.31, 
                         CTVA = 38.31, 
                         PINS = 68.21, 
                         UBER = 49.63, 
                         MRNA = 141.01, 
                         PENN = 70.03)
addrevenue$date %<>% as.Date()
revenue <- rbind(revenue, addrevenue)
rm(addrevenue)

total <- as.matrix(revenue[, 2:7]) %*% as.matrix(shareset) + rest
revenue$total <- as.vector(total)
rm(total)
revenue$ZMr <- revenue$ZM * shareset[1]
revenue$CTVAr <- revenue$CTVA * shareset[2]
revenue$PINSr <- revenue$PINS * shareset[3]
revenue$UBERr <- revenue$UBER * shareset[4]
revenue$MRNAr <- revenue$MRNA * shareset[5]
revenue$PENNr <- revenue$PENN * shareset[6]

revenue %<>% select(date, total, ZM, ZMr, CTVA, CTVAr, PINS, PINSr, UBER, UBERr, MRNA, MRNAr, PENN, PENNr)

# draw picture
ggplot(revenue, mapping = aes(x = date, y = total)) + 
  geom_line() + 
  ylab("revenue") + 
  xlab("month") + 
  ggtitle("The asset values every day") + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
kable(revenue[107, c(1, 2, 4, 6, 8, 10, 12, 14)])
```

Assume an initial position of \$250,000 in cash starting on 1 July 2020. At the end of 2020-12-01, we have a position of \$495,201 in cash.  

\newpage
## Shiny
In shiny we not only display the result of our portfolio, but also show close prices of the indexes and some other stocks.  
- You can choose from the sidebar to see the information of all stocks and our portfolio.  
- Information of all stocks contains the index information and various prices of a single stock from 2020-07-01 to 2020-12-01. In control box you can choose which period and stock to display.  
- We use tables and dynamic plots to show our portfolio.    
- We provide a way to build your own portfolio. You can choose 3 stocks and set different proportions, then track your portfolio.  

[Click here go to shiny app](https://rongli.shinyapps.io/FinalShiny/)


## Inference
- The main packages I use:  
1.Matt Dancho and Davis Vaughan (2020). tidyquant: Tidy Quantitative Financial
  Analysis. R package version 1.0.2. https://CRAN.R-project.org/package=tidyquant   
2.Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr:
  A Grammar of Data Manipulation. R package version 1.0.2.
  https://CRAN.R-project.org/package=dplyr  
3.Alboukadel Kassambara (2020). ggpubr: 'ggplot2' Based Publication Ready Plots.
  R package version 0.4.0. https://CRAN.R-project.org/package=ggpubr  
4.Stefan Milton Bache and Hadley Wickham (2014). magrittr: A Forward-Pipe
  Operator for R. R package version 1.5.
  https://CRAN.R-project.org/package=magrittr  
5.Hadley Wickham (2020). tidyr: Tidy Messy Data. R package version 1.1.2.
  https://CRAN.R-project.org/package=tidyr   
  
- The data I use is downloaded from [YAHOO](https://finance.yahoo.com/).  

- The online investment I use is from [ETF](https://www.etf.com/channels/ipo)  


